PK object batch mode trial

### 2023-08-09 data-raw/batchMode_trial_gpm.Rmd
Created testing vignette, updated rsq and fold_error for batch mode

>>>>

```{r function_connections}
fw <- mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                        border = TRUE, cex = 0.6, lwd = 1.5)
fun_mat <- fw$funmat

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "bp_test",
                  border = TRUE, cex = 1, lwd = 1.5)

fun_mat2 <- fun_mat[rowSums(fun_mat) > 0, ]

library(ComplexHeatmap)
ComplexHeatmap::Heatmap(fun_mat2, row_names_side = "left", column_names_side = "top",
                        row_names_gp = gpar(fontsize = 10),
                        column_names_gp = gpar(fontsize = 10),
                        col = circlize::colorRamp2(c(0, 1), colors = c("white", "green4")),
                        rect_gp = gpar(col = "black", lwd = 1),
                        show_row_dend = FALSE,
                        show_column_dend = FALSE)

fun_mat %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column(var = "from") %>%
  pivot_longer(cols = !from,
               names_to = "to",
               values_to = "Call") %>%
   mutate(
    from = str_remove(from, pattern = ".pk"),
    to = str_remove(to, pattern = ".pk")
  ) %>%
  filter(from %in% "residuals") %>% View()

fun_mat2 %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column(var = "from") %>%
  pivot_longer(cols = !from,
               names_to = "to",
               values_to = "Call") %>%
  filter(Call != 0) %>% 
  transmute(
    from = str_remove(from, pattern = ".pk"),
    to = str_remove(to, pattern = ".pk")
  ) %>%
  filter(from %in% c("residuals"),
         !(to %in% c("check_model",
                     "check_method",
                     "check_newdata",
                     "check_required_status"))) %>%
  ggflowchart::ggflowchart(horizontal = TRUE)
```
